---
title: "MGMT6550 Assignment 1: BBets"
author: "Carlos Pelayo"
date: "01/31/2020"
output: html_document: default
 ---


```{r setup,include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```


Test if push worked


<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have the same birthday.  Brownlow has made this bet 21 times, so far. Where do you think his profits are? Discuss this in a markdown document


# Methods
<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 21 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->

<!--PUT IN A CHUNK FOR A HISTOGRAM!-->
```{r}
days = 1:365
classSample= sample(days,35,replace=TRUE)
if (length(unique(classSample))==35){
  print('I Lose')
}else{print('I win')}

```


```{r}
days=1:365
bank=0
students=35
repeatn= 100
winnings=numeric()
for ( j in 1:repeatn)
  {classSample = sample(days,students,replace=TRUE)
  if (length(unique(classSample))==students)
  {bank = bank-2}
  else{bank=bank+1}
  winnings[j]=bank
  }
hist(winnings,xlab="Winnings ($)")

print(paste( 'Winnings =',winnings[repeatn]))
plot(winnings,type = 'l',col="red",xlab="Times Played",ylab="Winnings ($)")
```


# Profit Estimate

<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows net position after betting !-->


# Confidence interval of Brownlows earning

<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlow's net financial position !-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.

Would you take this bet?  What about if there were only 12 people in the class?   !-->

